---
title: "Predicition Assignment"
output: html_document
---

##Prediction Assignment - Practical Machine Learning Coursera
Michael D
04 January 2021

##Overview
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

```{r}
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
library(gbm)
library(plyr)
library(rattle)

set.seed(12345)
 
##Cleaning the Data
download.file(url = "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", 
              destfile = "./pml-training.csv", method = "curl")

dt_training <- read.csv("./pml-training.csv", na.strings=c("NA","#DIV/0!",""))

download.file(url = "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", 
              destfile = "./pml-testing.csv", method = "curl")

dt_testing <- read.csv("./pml-testing.csv", na.strings=c("NA","#DIV/0!",""))

features <- names(dt_testing[,colSums(is.na(dt_testing)) == 0]) [8:59]

dt_training <- dt_training[,c(features,"classe")]
dt_testing <- dt_testing[,c(features, "problem_id")]

dim(dt_training); dim(dt_testing);

set.seed(12345)

inTrain <- createDataPartition(dt_training$classe, p=0.6, list=FALSE)
training <- dt_training[inTrain,]
testing <- dt_training[-inTrain,]

dim(training); dim(testing);

##Decsision Tree Model
modFitDT <- rpart(classe ~ ., data = training, 
                  method="class", control = rpart.control(method = "cv", number = 10))
fancyRpartPlot(modFitDT)
```
```{r}
##Decision Tree Prediction
prediction <- predict(modFitDT, testing, type = "class")
test_classe <- as.factor(testing$classe)
confusionMatrix(prediction, test_classe)

##Random Forest Model
training$classe <- as.factor(training$classe)
modFitRF <- randomForest(classe ~ ., data = training, method = "rf", importance = T, trControl = trainControl(method = "cv", classProbs=TRUE,savePredictions=TRUE,allowParallel=TRUE, number = 10))

plot(modFitRF)
```
```{r}
##Random Forest Predicition
prediction <- predict(modFitRF, testing, type = "class")
test_classe <- as.factor(testing$classe)
confusionMatrix(prediction, test_classe)

##Boosting Model
modFitBoost <- train(classe ~ ., method = "gbm", data = training,
                     verbose = F,
                     trControl = trainControl(method = "cv", number = 10))

modFitBoost

plot(modFitBoost)

##Boosting Model Predicition
prediction <- predict(modFitBoost, testing)
test_classe <- as.factor(testing$classe)
confusionMatrix(prediction, test_classe)
```


##Predicition of Test Data
#Decision Tree
```{r}
predictionDT <- predict(modFitDT, dt_testing)
predictionDT
#RandomForest
predictionRF <- predict(modFitRF, dt_testing)
predictionRF
#Boost
predictionBoost <- predict(modFitBoost, dt_testing)
predictionBoost

```
